Natural variation in teosinte at the domestication locus teosinte branched1 (tb1)

### 2014-04-30 manuscript.tex
edits + TP comments on .pdf

The phenotypic effects of the Hopscotch insertion in domesticated maize have been well documented \citep{Clark2006, Studer2011}, \jri{did clark do phenotyping?} and \citet{Weber2007} have described its effects in partially inbred lines of teosinte \citep{Weber2007} \jri{i don't think these were inbred.please doublecheck.}. Our study is the first to explicitly examine the phenotypic effects of the Hopscotch insertion in individuals sampled from a natural population of teosinte. \jri{isn't this what weber did?? for 70+ populations!?} However, we found no significant effect of the Hopscotch on tillering index or tiller number in our phenotyping experiments, and the effect of the Hopscotch insertion in teosinte is discordant with that of maize. The lack of correlation between Hopscotch genotype and tillering index or tiller number is surprising given its effects in maize. It is certainly possible that even though previous data demonstrate an effect of the Hopscotch on tillering in maize \citep{Studer2011}, that the effect of the Hopscotch in teosinte is more complicated and may be more difficult to observe. Moreover, \emph{tb1} is a single gene in a complex pathway that affects branching and tillering traits, and perhaps in combination with alleles at other loci the phenotypic effects of the Hopscotch on tillering may not be consistent. \jri{thsi section still needs work. i think we have to do more here. weber shows an association between SNPs in tb1 and branch length. we need to discuss that!}

>>>>

The phenotypic effects of the Hopscotch insertion in domesticated maize have been well documented \citep{Clark2006, Studer2011}, \jri{did clark do phenotyping?} \lev{yes they phenotyped their bc1 i believe, 8 traits shown to correlate with tb1 variation} and \citet{Weber2007} have described its effects in partially inbred lines of teosinte \citep{Weber2007} \jri{i don't think these were inbred.please doublecheck.}. Our study is the first to explicitly examine the phenotypic effects of the Hopscotch insertion in individuals sampled from a natural population of teosinte. \jri{isn't this what weber did?? for 70+ populations!?} However, we found no significant effect of the Hopscotch on tillering index or tiller number in our phenotyping experiments, and the effect of the Hopscotch insertion in teosinte is discordant with that of maize. The lack of correlation between Hopscotch genotype and tillering index or tiller number is surprising given its effects in maize. It is certainly possible that even though previous data demonstrate an effect of the Hopscotch on tillering in maize \citep{Studer2011}, that the effect of the Hopscotch in teosinte is more complicated and may be more difficult to observe. Moreover, \emph{tb1} is a single gene in a complex pathway that affects branching and tillering traits, and perhaps in combination with alleles at other loci the phenotypic effects of the Hopscotch on tillering may not be consistent. \jri{thsi section still needs work. i think we have to do more here. weber shows an association between SNPs in tb1 and branch length. we need to discuss that!}
